\vspace{-1cm}\normalsize{\textbf{Fairly Random: Impact of Winning the Toss on the Probability of Winning}}

### 2016-03-06 write_up/cricket.tex
figure formatting

\begin{figure}[htbp]
\caption{Difference in Winning Percentages of Teams that Won the Toss and Teams that Lost the Toss by Type of Match.}
\begin{minipage}{0.85\textwidth}
\centering
\includegraphics[scale=.85]{../figs/winbyType.pdf}
{\footnotesize Note: Means and 95\% confidence intervals. \emph{n} refers to the number of matches.\par}
\end{minipage}
\label{fig:type}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\caption{Difference in Winning Percentages of Teams that Won the Toss and Teams that Lost the Toss by Day or Day and Night}
\includegraphics[scale=.85]{../figs/winbyDayNight.pdf}
{\footnotesize Note: Means and 95\% confidence intervals. \emph{n} refers to the number of matches.\par}
\label{fig:dn}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\caption{Difference in Winning Percentages of Teams that Won the Toss and Teams that Lost the Toss by Month in England}
\includegraphics[scale=.85]{../figs/winbyMonthEngland.pdf}
{\footnotesize Note: Means and 95\% confidence intervals. \emph{n} refers to the number of matches.\par}
\label{fig:season}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\caption{Difference in Winning Percentages of Teams that Won the Toss and Teams that Lost the Toss by Whether or not Duckworth-Lewis was invoked}
\includegraphics[scale=.85]{../figs/winbyDL.pdf}
{\footnotesize Note: Means and 95\% confidence intervals. \emph{n} refers to the number of matches.\par}
\label{fig:dl}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\caption{Difference in Winning Percentages of Teams that Won the Toss and Teams that Lost the Toss by Country}
\includegraphics[scale=.85]{../figs/winbyCountry.pdf}
{\footnotesize Note: Means and 95\% confidence intervals. \emph{n} refers to the number of matches.\par}
\label{fig:country}
\end{figure}

>>>>

\begin{figure}[htbp]
\caption{Difference in Winning Percentages of Teams that Won the Toss and Teams that Lost the Toss by Type of Match.}
\centering
\includegraphics[scale=.85]{../figs/winbyType.pdf}
{\footnotesize \\ Note: Means and 95\% confidence intervals. \emph{n} refers to the number of matches.\par}
\label{fig:type}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\caption{Difference in Winning Percentages of Teams that Won the Toss and Teams that Lost the Toss by Day or Day and Night}
\includegraphics[scale=.95]{../figs/winbyDayNight.pdf}
{\footnotesize \\ Note: Means and 95\% confidence intervals. \emph{n} refers to the number of matches.\par}
\label{fig:dn}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\caption{Difference in Winning Percentages of Teams that Won the Toss and Teams that Lost the Toss by Month in England}
\includegraphics[scale=1]{../figs/winbyMonthEngland.pdf}
{\footnotesize \\ Note: Means and 95\% confidence intervals. \emph{n} refers to the number of matches.\par}
\label{fig:season}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\caption{Difference in Winning Percentages of Teams that Won the Toss and Teams that Lost the Toss by Whether or not Duckworth-Lewis was invoked}
\includegraphics[scale=1]{../figs/winbyDL.pdf}
{\footnotesize \\ Note: Means and 95\% confidence intervals. \emph{n} refers to the number of matches.\par}
\label{fig:dl}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\caption{Difference in Winning Percentages of Teams that Won the Toss and Teams that Lost the Toss by Country}
\includegraphics[scale=1]{../figs/winbyCountry.pdf}
{\footnotesize \\ Note: Means and 95\% confidence intervals. \emph{n} refers to the number of matches.\par}
\label{fig:country}
\end{figure}
